This section describes how the ARM7 port of EFSL works. This documentation was written
by Martin Thomas, as is the port to the ARM7 and the examples included with EFSL.
The examples are pretty large, so we will not print them here, they have their own
subdirectory in the examples sections and should be quite understandable.

Please note that the LPC2000 and AT91SAM7 interfaces are Copyright (c) by Martin Thomas, Kaiserslautern, Germany.

\subsubsection{License}
The LPC2000- and AT91SAM7-interface inherit the license from the main efsl-source.

\subsubsection{General information about the ARM interfaces}
	\begin{itemize}
	
\item The current version of the EFSL includes SD-interfaces
for the LPC2000 ARM7TDMI-S controllers from NXP(Philips) and 
the AT91SAM7 ARM7TDMI controllers from Atmel. The ARM-core 
of these devices is basicly the same but the integrated
SPI-hardware from NXP and Atmel is not compatible. So
a different set of interface-functions is needed for each
family.

\item A GNU arm-elf toolchain/cross-compiler
must be available to build the examples
and the library.

\item \code{\#define BYTE\_ALIGNMENT} is disabled
for the LPC-interace in config.h 
It didn't work with alignment enabled.

\item Buffers can be configured as
described in the efsl-manual.

\item The hardware connection is similar 
to the connection described
in this manual for Atmel AVRs.
(I (M.~Thomas) have mounted the pullups in some of my
test-systems but tests have been done 
successfully without pull-up resistors)
	\end{itemize}

\subsubsection{Additional information about the LPC2000 interface}
	\begin{itemize}

\item The interface supports SD-Cards
connected to the LPC2000 SPI ("SPI0") 
and SSP ("SPI1") interface. The SPI-
interface is hardcoded by the value 
defined in config.h and can not be 
changed during runtime.

\item Only some parts of the LPC2000-family
have the fast SSP-Interface (i.e. LPC213x,
LPC214x) others only provide the slower 
SPI interface.

\item To build the library create the file 
conf/config.h based on the template 
config-sample-lpc2000.h and use the 
makefile Makefile-LPC2000 in the
efsl-root-directory for LPC2000s 
(ARM7TDMI-S).

\item So far the interface has only been
tested with LPC2138- and LPC2148-controllers
and the SPI(0) and SSP-Interface.
Other LPC2000-ARM7 controllers 
should be supported too. Verify
that the register-adresses in 
inc/interfaces/LPC2000\_regs.h
match the used controller and the
maximum speed defined in lpc2000\_spi.c
is available for the part.
Verify the pin-connections in lpc2000\_spi.c.
	\end{itemize}


\subsubsection{Additional information about the AT91SAM7 interface}
	\begin{itemize}
	
\item The interface supports SD-Cards connected 
to the AT91SAM7 SPI interface. 

\item To build the library create a file 
conf/config.h based on the template 
config-sample-at91.h and use the 
makefile Makefile-AT91 in the
efsl-root-directory for AT91 (ARM7TDMI).

\item The AT91SAM7 offers 4 chip-select
signals which can be mapped to
different pins. Chip-select is done
by the hardware. See at91_spi.c
for configuration options.
Chip-Select can be fixed or variable
(Fixed or variable peripheral select - see 
option in AT91\_spi.c, further information 
in the datasheet).

\item I have tested the interface with  AT91SAM7S256 
and SAM7S64 controllers. Other AT91-ARM7 controllers 
should be supported too.
To adapt the code for another AT91 with SPI:
		\begin{itemize}
\item check if the register-defintions in AT91SAM7S\_regs.h 
are valid for the target. The file can be replaced
by header file provided by Atmel for the used part 
(see at91.com)
\item verify the maximum speed in at91_spi.c
\item verfiy the pin-connections in at91_spi.c
\item Check the memory-settings in the linker-script of
the example.
		\end{itemize}
	\end{itemize}


\subsubsection{Example code}

For each interface an example application is provided in the 
examples-directory. The examples can be build with the library 
libefsl.a or with the efsl source-code.

\begin{enumerate}

\item using the EFSL source-code in the project:

	\begin{itemize}

\item Verfiy that conf/config.h is present
and the settings match the used 
interfaces (see templates).

\item Modify the line in the example's 
Makefile to: EFSL_AS_LIB = 0

\item "make all" in the example's directory.

	\end{itemize}


\item using the EFSL library (libefsl.a) in the project:

	\begin{itemize}

\item Verfiy that conf/config.h is present
and the settings match the used 
interfaces (see templates).

\item Build the library libefsl.a with
the Makefile from the efsl root-
directory for the used interface.
(i.e. "make --makefile=Makefile-AT91 lib" 
or "make --makefile=Makefile-LPC2000 lib" )

\item Modify the line in the example's 
Makefile to: EFSL\_AS\_LIB = 1

\item "make all" in the example's directory
	\end{itemize}

\end{enumerate}


The example-applications demonstrate:
	\begin{itemize}
\item Init of the EFSL ARM debug-system
\item Init of the EFSL
\item List contents of the SD-Card's
root directory
\item Open a file and type the content
\item Append a line of text to a file
\item "cat/type" the file's content again
	\end{itemize}

The example applications print status- and 
debug-messages to the UART1 on LPC2000 or DBGU on AT91SAM7
(115200,8,N,1,no FC).


\subsubsection{Test Hard- and Software}
	\begin{itemize}

\item Keil (keil.com) MCB2130 board with LPC2138
with additional SD/MMC-connector (from Buerklin.de)

\item Atmel AT91SAM7S-EK board with AT91SAM7S64
with additional SD/MMC-connector

\item SAM7-P board with AT91SAM7S256
with on-board SD/MMC-connector

\item SanDisk "standard" SD-Card 256MB
(not the "highspeed"-version)

\item WinARM (arm-elf GNU toolchain)

\item Bray++ Terminal

	\end{itemize}


\subsubsection{Credits}

\begin{itemize}

\item The code in efsl_debug_printf_arm.c is 
based on code from Holger Klabunde
and has been modified to support
a "fdevopen"-function (efsl_debug_devopen_arm). 
The original code has no copyright-notice and
is derived from an free code by Volker Oth.

\item Register-definitions for LPC213x are 
based on a header-file from Keil (an ARM-company) 
(supplied with the DKARM trial-version).

\item Register-definitions for AT91SAM7 are from 
at91.com (provided by Atmel).

\item The basic method to handle the SPI interface
on AT91 has been found in a free example from 
olimex.com.

\end{itemize}
